Proportional multi-state multiple-cohort life table model

### 2018-04-03 MSLT/MSLTdoc.Rmd
Added inputs table

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing
output:
  pdf_document: 
    toc: true
    number_sections: true
    fig_caption: yes
  fontsize: 12 pt
  geometry: margin=1in

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction

@@

## Inputs (ADD A SUMMARY TABLE with inputs and potential sources of data)

@@

####	Total prevalent years lived with disability rates per single year and sex.

@@

```{r, echo=FALSE}
pmslt_inputs <- matrix(c(1:15), ncol = 3, byrow = TRUE)
colnames(pmslt_inputs) <- c("Input", "Source", "Comments")
rownames (pmslt_inputs) <- c("Population numbers", "Death rates", "Years lived with disability rates", "Disease epidemilogy", "Disability weights")
print(pmslt_inputs)
```

>>>>

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing

output:
  pdf_document: 
    toc: true
    number_sections: true
    fig_caption: yes
  fontsize: 12 pt
  geometry: margin=1in

@@

```{r setup, include=FALSE}

#Global options
knitr::opts_chunk$set(echo = TRUE)

#Packages to run code
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
options(knitr.table.format = 'latex')
```
# Introduction

@@

## Inputs

@@

####	Total years lived with disability rates per single year and sex.

@@

```{r, echo=FALSE}
pmslt_inputs <- tribble(
~Input, ~Source, ~Comments, 
"Life table", "Synthetic population per sex and age group", "Age grouping in life table to match synthetic population", 
"Life table", "Synthetic population per sex and one-year age group", "If one year age group is not avabilable it can be derive using interpolation from age groups data", 
"Life table", "Global Burden of Disease (GBD) study per one-year age group and sex", "GBD data is in five-year age groups, interpolation to derive one-year age groups", 
"Disease life table", "GBD data for prevalence, incidence and mortality and DISMOD II", "Two step process. First obtain disease and population data from GBD. Second, use Dismod II to derive internally consistent estimates for incidence and case fatality (PMSLT disease life table iputs", 
"Disease life table", "Derive from disease prevalence and years lived with disability from GBD", "Adjustments for comorbidities in later years of life to be applied"
)

kable(pmslt_inputs,"latex", booktabs = T, caption = "PMSLT inputs") %>%
 kable_styling(latex_options = c("striped", "hold_position"),
               full_width = F)%>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "20em")
```
